Fig 2

### 2020-08-21 analysis/figure-2.Rmd
typos

b <- makebargraphv3(DEGcontrol, "hypothalamus","No. of DEGs\n(-) decreased  increased (+)", comparisonlabelscontrol) +
  labs(x = "Control versus all other reproductive and parental stages",
       title = "Hypothalamus") +
  geom_rect(mapping=aes(xmin=0.5, xmax=1.5, ymin=-1000, ymax = 350, fill = F), color="black", alpha=0.5) +
  annotate("text", x = 1, y = -1075, label = "D", size = 2.5)

@@

b <- makebargraphv3(DEGcontrol, "pituitary","No. of DEGs\n(-) decreased  increased (+)", comparisonlabelscontrol) +
  labs(x = "Control versus all other reproductive and parental stages",
       title = "Pituitary")

@@

b <- makebargraphv3(DEGcontrol, "gonad","No. of DEGs\n(-) decreased  increased (+)", comparisonlabelscontrol) +
  labs(x = "Control versus all other reproductive and parental stages",
       title = "Pituitary")

>>>>

b <- makebargraphv3(DEGcontrol, "hypothalamus","No. of DEGs\n(-) decreased  increased (+)", comparisonlabelscontrol) +
  labs(x = "Control versus all other reproductive and parental stages") +
  geom_rect(mapping=aes(xmin=0.5, xmax=1.5, ymin=-1000, ymax = 350, fill = F), color="black", alpha=0.5) +
  annotate("text", x = 1, y = -1075, label = "D", size = 2.5)

@@

b <- makebargraphv3(DEGcontrol, "pituitary","No. of DEGs\n(-) decreased  increased (+)", comparisonlabelscontrol) +
  labs(x = "Control versus all other reproductive and parental stages")

@@

b <- makebargraphv3(DEGcontrol, "gonad","No. of DEGs\n(-) decreased  increased (+)", comparisonlabelscontrol) +
  labs(x = "Control versus all other reproductive and parental stages")
